---
title: "Homework 5"
author: "Kairui Wang"
date: "2023-11-05"
output: github_document
---

```{r, include = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

```

Load key packages.

```{r,message = FALSE}
library(tidyverse)
library(rvest)
library(broom)
library(plotly)
```

Set seed for reproducibility.

```{r}
set.seed(12345)
```


## Problem 1

Read the dataset from the corrected URL

```{r}
data_url <- "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"
homicide_data <- read_csv(data_url)
```

Describe the raw data:

```{r}
glimpse(homicide_data)
head(homicide_data)
```

Create a city_state variable and summarize the data within cities

```{r}
sum_homicide_data <- 
  homicide_data |> 
  mutate(city_state = paste(city, state, sep = ", ")) |> 
  group_by(city_state) |> 
  summarize(
    total_homicides = n(),
    unsolved_homicides = sum(disposition %in% c("Closed without arrest", "Open/No arrest"))
  ) |> 
  ungroup()

print(sum_homicide_data)
```

Filter the data for Baltimore, MD

```{r}
baltimore_data <- 
  homicide_data |> 
  filter(city == "Baltimore" & state == "MD")
```

Use prop.test to estimate the proportion of unsolved homicides

```{r}
prop_test_result <- 
  prop.test(
  sum(baltimore_data$disposition %in% c("Closed without arrest", "Open/No arrest")),
  nrow(baltimore_data)
)
```

Apply broom::tidy to the prop.test result

```{r}
baltimore_tidy <- 
  tidy(prop_test_result)
```

Extract the estimated proportion and confidence intervals

```{r}
baltimore_proportion <- baltimore_tidy$p.value
baltimore_conf_interval <- prop_test_result$conf.int
```

Print the results

```{r}
print(baltimore_tidy)
```

Create a list column for each city and apply prop.test

```{r}
result_df <- 
  homicide_data |> 
  group_by(city) |> 
  nest() |> 
  mutate(
    prop_test_result = map(data, ~ prop.test(
      sum(.x$disposition %in% c("Closed without arrest", "Open/No arrest")),
      nrow(.x)
    )),
    tidy_results = map(prop_test_result, broom::tidy)
  ) |> 
  unnest(tidy_results) |> 
  select(city, estimate, conf.low, conf.high)

print(result_df)

```

Create a plot

```{r}
result_df |> 
  mutate(city = fct_reorder(city, estimate)) |> 
  ggplot(aes(x = estimate, y = city)) +
  geom_point(size = 3) +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.2) +
  labs(
    x = "Proportion of Unsolved Homicides",
    y = "City",
    title = "Proportion of Unsolved Homicides by City",
    subtitle = "Estimates and Confidence Intervals"
  ) +
   theme_minimal()

```



